### 2019-02-15 abstract.tex
retouche
version2_rapport

\begin{center}
	\par
	\textbf{
		\vskip 0.5in
		\LARGE 
			Résumé \\[0.15in]
			\addcontentsline{toc}{chapter}{\numberline{}Résumé}
	}
\end{center}
	\par

@@

\newpage
\begin{center}
	\par
	\textbf{
		\vskip 0.5in
		\LARGE 
			Abstract \\[0.15in]
	}
\end{center}
	\par

    We live in a world where the amount of information is constantly increasing and whose good management involves the use of graphs that have spread in different fields from social and communication networks to the fields of chemistry and biology. This abundance of generated data calls for a technique that is as old as the discipline of data processing but which is facing new challenges today: the compression. Graph compression is a field in which the initial graph undergoes transformations in order to obtain a smaller and more compact version allowing, in the majority of cases, to perform the treatments in a much better time.

>>>>

\thispagestyle{plain}
\begin{center}
	\par
	\textbf{
		\vskip 0.5in
		\LARGE 
			Résumé \\[0.15in]
			\addcontentsline{toc}{chapter}{\numberline{}Résumé}
	}
\end{center}
	\par

@@

\newpage
\thispagestyle{plain}
\begin{center}
	\par
	\textbf{
		\vskip 0.5in
		\LARGE 
			Abstract \\[0.15in]
	}
\end{center}
	\par

    We live in a world where the amount of information is constantly increasing and whose good management involves the use of graphs that have spread in different fields from social and communication networks to the fields of chemistry and biology. This abundance of generated data calls for a technique that is as old as the discipline of data processing but which is facing new challenges today: compression. Graph compression is a field in which the initial graph undergoes transformations in order to obtain a smaller and more compact version allowing, in the majority of cases, to perform the processings in a much better time.
